\begin{frame}[allowframebreaks, fragile]{Tài liệu tham khảo}
\begin{thebibliography}{00}

% 1
\bibitem{vaswani2017attention}
Vaswani, A., Shazeer, N., Parmar, N., Uszkoreit, J., Jones, L., Gomez, A. N., Kaiser, L., \& Polosukhin, I. (2017). Attention is all you need. \textit{Advances in neural information processing systems}, 30. \url{http://arxiv.org/abs/1706.03762}

% % 4
% \bibitem{ddd-evans}
% Evans, E. (2004). \textit{Domain-Driven Design: Tackling Complexity in the Heart of Software}. Addison-Wesley Professional.

% % 7
% \bibitem{outbox-pattern}
% Richardson, C. \textit{Pattern: Transactional outbox}. Microservices.io. Truy cập ngày 28/06/2026, từ \url{https://microservices.io/patterns/data/transactional-outbox.html}

% 8
\bibitem{aws-rag}
Amazon Web Services. \textit{Retrieval-Augmented Generation (RAG) là gì?}. Truy cập ngày 28/06/2026, từ \url{https://aws.amazon.com/vi/what-is/retrieval-augmented-generation}

% 9
\bibitem{weaviate-rag}
Weaviate. \textit{What is Agentic RAG?}. Truy cập ngày 28/06/2026, từ \url{https://weaviate.io/blog/what-is-agentic-rag}

% 10
\bibitem{dlthub}
dltHub. \textit{Introduction to dlt}. Truy cập ngày 28/06/2026, từ \url{https://dlthub.com/docs/intro}

% 11
\bibitem{scrapy}
Scrapy. \textit{A Fast and Powerful Scraping and Web Crawling Framework}. Truy cập ngày 28/06/2026, từ \url{https://www.scrapy.org}

% 14
\bibitem{vietnamese-sbert}
Hugging Face. \textit{vietnamese-sbert}. Truy cập ngày 28/06/2026, từ \url{https://huggingface.co/keepitreal/vietnamese-sbert}

% 15
\bibitem{langchain-vectorstores}
LangChain. \textit{Vector stores}. Truy cập ngày 28/06/2026, từ \url{https://docs.langchain.com/oss/python/integrations/vectorstores}

% 16
\bibitem{langgraph}
LangChain. \textit{LangGraph Overview}. Truy cập ngày 28/06/2026, từ \url{https://docs.langchain.com/oss/python/langgraph/overview}

% 17
\bibitem{ddd-hexagon}
Sairyss. \textit{Domain-Driven Hexagon}. GitHub. Truy cập ngày 28/06/2026, từ \url{https://github.com/Sairyss/domain-driven-hexagon#diagram}

% % 19
% \bibitem{kong-gateway}
% Kong. \textit{Kong Gateway}. Truy cập ngày 28/06/2026, từ \url{https://developer.konghq.com/gateway}

% % 22
% \bibitem{supabase-jwts}
% Supabase. \textit{JSON Web Tokens (JWTs)}. Truy cập ngày 28/06/2026, từ \url{https://supabase.com/docs/guides/auth/jwts}

% % 23
% \bibitem{neon-postgrest}
% Neon. \textit{Create a REST API from Postgres with PostgREST}. Truy cập ngày 28/06/2026, từ \url{https://neon.com/docs/guides/postgrest}

% % 24
% \bibitem{heroku-docker}
% Heroku. \textit{Deploying with Docker}. Truy cập ngày 28/06/2026, từ \url{https://devcenter.heroku.com/categories/deploying-with-docker}

% 52
\bibitem{dlthub-how-it-works}
dltHub. \textit{How dlt works}. Truy cập ngày 28/06/2026, từ \url{https://dlthub.com/docs/reference/explainers/how-dlt-works}

\end{thebibliography}

% \note{
% 123
% }
\end{frame}
